---
title: "A test with conllu.js in R"
author: Niko Partanen
output:
  html_document:
    includes:
      after_body: after_body.html
      in_header: header.html
    section_divs: FALSE
    lib_dir: lib
    self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is a test with using [conllu.js](http://spyysalo.github.io/conllu.js/) JavaScript library within an RMarkdown document, so that it would be easy to embed UD examples into HTML documents. conllu.js allows displaying graphically trees annotated in CoNLL-U format. The library is done by Sampo Pyysalo. All JavaScript, CSS and HTML files are more less directly taken from the examples on [conllu.js](http://spyysalo.github.io/conllu.js/) website. 

For this experiment, a more complete version would have different output for PDF and HTML, but now this is mainly my personal testing. There are also lots of possibilities to modify the Edit-button, as there could be all kind of additional information such as citation info.

## Examples

```{r, results='asis'}
suppressPackageStartupMessages(library(tidyverse))
library(conllr)

uig <- read_conll('https://raw.githubusercontent.com/UniversalDependencies/UD_Uyghur/master/ug-ud-dev.conllu')

uig %>% 
  filter(id == 's901') %>%
  as_conllu_div()

```

Ok, so that works fine. The only problem is that there doesn't seem to be any API to retrieve individual UD example sentences by language and ID. If I want to discuss one Finnish or Russian example, I don't want to read the whole files, but could ideally just retrieve the one I need.
