---
title: "Komi-Zyrian UD corpus"
author: Niko Partanen
output:
  html_document:
    includes:
      after_body: after_body.html
      in_header: header.html
    section_divs: FALSE
    lib_dir: lib
    self_contained: no
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a HTML display into the trees annotated within upcoming Universal Dependencies Komi-Zyrian corpus. The work has been coordinated by Niko Partanen in LATTICE laboratory, but there have been several participants. The work connects closely to multilingual dependency parsing approach currently being developed in LATTICE. In case there are comments of questions, please contact Niko Partanen (nikotapiopartanen@gmail.com).

```{r, results='asis', echo=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(conllr)
library(purrr)
library(purrrlyr)

kpv <- read_conll('https://raw.githubusercontent.com/langdoc/UD_Komi-Zyrian/master/kpv-ud-test.conllu')

kpv %>% 
  distinct(id) %>% 
  pull(id) %>%
  map(~ kpv %>% filter(id == .x) %>%
        as_conllu_div()) %>%
  shiny::div()

```
